Renaming The Amplicons and Tidying up the Amplicon Information Table

### 2024-06-18 extras/Renaming-amplicons/Amplicon-renaming.Rmd
Cleaning up some stuff

>>>>

### As an aside:

To process these things in the snakemake mega-simple workflow, we will add a new
field that goes within `genome` or `target_fasta` in the config file which is called
`rename:` and that give tsv file with columns named `orig` and `new` which are the
original names and the desired new names, and we will make one extra rule in there
somehow to deal with it.  We will keep the VCFs with the original names, but we need
a rule that will make a renamed VCF, and we also need a renamed Microhaplot output.

So we won't change the target fastas.  This way we have a data set that is compatible
with old stuff, and we also have one that we can use with the new names.
